Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-04-20 draft/paper1.tex
Update the sample stats. figure
Update the SED related figures

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:mass_complete}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \begin{center}
        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_2.pdf}
        \caption{
            Relationships between \mstar{} and other stellar population 
            parameters using the results from \texttt{iSEDfit}. 
            The \textbf{left} figures are for the \rbcg{} sample, and the 
            \textbf{righ}t ones are 
            for the \nbcg{} sample. 
            They are both color-coded using the redshift of the object, while 
            their sizes reflect the magnitude differences in $i$-band between 
            the observed and best-fit value. 
            The four stellar population properties are: 
            1) \textbf{Top-left}: mass-weighted stellar age in Gyr; 
            2) \textbf{Bottom-left}: \m2l{} in $i$-band; 
            3) \textbf{Top-right}: mass-weighted stellar metallicity in unit of Solar 
            value;
            4) \textbf{bottom-right}: dust extinction values in magnitude.
            }
        \label{fig:ised_2}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \begin{center}
        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_3.pdf}
        \caption{
            Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
            assumptions. 
            In each figure, we plot the \mstar{} from default model against their 
            differences with other models. 
            The top (bottom) row shows the comparisons of the \rbcg{} (\nbcg{}) sample. 
            The four models involved here are labeled as: 
            (A): default one; 
            (B): using the Salpeter IMF instead of the Chabrier one 
                (\textbf{Left column});
            (C): using the BC03 synthetic population model instead of the FSPS one
                (\textbf{Middle column});
            (D): assume that there is no dust extinction (\textbf{Right column}). 
            On each figure, the grey shaded region highlights the uncertainty 
            of the $\log($\logms{}$)$ using typical \mstar{} uncertainties from 
            both sides. 
            For each comparison, we highlight the median $\chi^{2}$ value, and the fraction
            of galaxies with $\chi^{2} > 10.0$ at the top. 
            We also show the histogram of the \mstar{}-differences on the right panel.
            }
        \label{fig:ised_3}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:mass_complete}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
          \song{Update the caption}
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \begin{center}
        \includegraphics[width=12cm]{fig/redbcg_isedfit_2.pdf}
        \caption{
            \song{Update the caption.}
            Relationships between \mstar{} and other stellar population 
            parameters using the results from \texttt{iSEDfit}. 
            The \textbf{left} figures are for the \rbcg{} sample, and the 
            \textbf{righ}t ones are 
            for the \nbcg{} sample. 
            They are both color-coded using the redshift of the object, while 
            their sizes reflect the magnitude differences in $i$-band between 
            the observed and best-fit value. 
            The four stellar population properties are: 
            1) \textbf{Top-left}: mass-weighted stellar age in Gyr; 
            2) \textbf{Bottom-left}: \m2l{} in $i$-band; 
            3) \textbf{Top-right}: mass-weighted stellar metallicity in unit of Solar 
            value;
            4) \textbf{bottom-right}: dust extinction values in magnitude.
            }
        \label{fig:ised_2}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure}
        \begin{center}
        \includegraphics[width=\columnwidth]{fig/redbcg_isedfit_3.pdf}
        \caption{
            \song{Update the caption.}
            Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
            assumptions. 
            In each figure, we plot the \mstar{} from default model against their 
            differences with other models. 
            The top (bottom) row shows the comparisons of the \rbcg{} (\nbcg{}) sample. 
            The four models involved here are labeled as: 
            (A): default one; 
            (B): using the Salpeter IMF instead of the Chabrier one 
                (\textbf{Left column});
            (C): using the BC03 synthetic population model instead of the FSPS one
                (\textbf{Middle column});
            (D): assume that there is no dust extinction (\textbf{Right column}). 
            On each figure, the grey shaded region highlights the uncertainty 
            of the $\log($\logms{}$)$ using typical \mstar{} uncertainties from 
            both sides. 
            For each comparison, we highlight the median $\chi^{2}$ value, and the fraction
            of galaxies with $\chi^{2} > 10.0$ at the top. 
            We also show the histogram of the \mstar{}-differences on the right panel.
            }
        \label{fig:ised_3}
        \end{center}
    \end{figure}
%% ------------------------------------------------------------------------------------ %%
